Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-10 volunteer-clouds-ieee-ci-si.tex
Revisio of the intro and SoA
With deletion of completed comments.

The rest of the paper is organized as follows: Next we present the
state of the art (Section \ref{sec:soa}) in web-based distributed
computation systems along with attempts to predict and model its behavior. %FERGU: El IEEE es americano
Then, a detailed description of the proposed system is presented
in Section \ref{sec:description}, followed by the experiments and
obtained results in Section \ref{sec:experiments}.
Finally, conclusions and future work are presented in Section \ref{sec:conclusion}.

@@

Fulfilling these properties could be achieved using any of the
languages, and associated technologies, mentioned above, provided that the user had
installed the required virtual machine plugin first, but with the advantage of
providing a single and universal way of accessing resources via an
URI, something that is not guaranteed using desktop
applications. Baratloo et al. tried in 1996 to create a system with
the aforementioned qualities called {\em Charlotte}
\cite{baratloo1996charlotte}. This system, which implemented a
distributed shared memory, was inspired by previous work
on parallel computing systems PVM and MPI and solved most issues by
using the Java virtual machine embedded in the browser,
which provides
security to the user, uniformity of computing environment
independently of the operating system and access to a common data store in the
server. Since the virtual machine is a sandbox, it is safe to the user
and running a compiled bytecode guarantees a certain level of
performance.
 Other issues such as scheduling, which are related to adaptive
 parallelism, are solved on the server. This
paper was later extended and published in a journal in 1999
\cite{baratloo1999charlotte}, but it is interesting to note that
already in the early stages of the web the possibility of
browser-based distributed computing was already researched.

@@

Recent works propose the use of cloud computing services for the components of
client-server distributed EAs. Cloud resources
can reduce operational costs by outsourcing both hardware and software maintenance
to the cloud provider. Another advantage is that they enable the provisioning of computing resources beyond what
is available in most laboratories, allowing researches to
scale algorithms at reasonable costs. Researchers have proposed the use of
public clouds such as Amazon EC2 \cite{CloudScale}, Google App Engine\cite{di2013towards}
and DropBox~\cite{mericloud}. The use of JavaScript to implement
server side components
gives software developers certain advantages in the cloud
paradigm, since is a first-classe citizen
in most Platforms as a Service (PaaS) products as most support the Node.js
framework \cite{wood13:nodejs:paas}. Many web services
have native JavaScript libraries too, and use JSON (JavaScript Object Notation) for data
interchange. Another advantage is that
developers can use the same software tools for both client and server
side development.
% Ayuda con la mini conclusion FERGU: mira la última frase de arriba
% Borrada por iterativa - JJ

@@

In the work presented in this paper, JavaScript has been used throughout the full
stack, which has the advantage of using the self-same lines of code for
writing an evolutionary algorithm for the
desktop or command line and browser clients, both based in the EC
library NodEO \cite{DBLP:conf/gecco/GuervosVGES14}. This saves time % [Mario] Creo que si se debería
% dedicar una oración para recordar la diferencia y relación entre NodIO y NodEO
% En mi mente los digo igual, NodEO como Rodeo y NodIO como Radio y me costó trabajo ver la diferencia
% Pero igual un lector que llegue a leer sin vicios, si vea claramente la relación.
when writing code and leverages %FERGU: qué diferencias hay entre NodIO y NodEO??
expertise acquired in the library itself. %FERGU: tienes info de LoC
                                %usadas para la sección experimental y
                                %justificar esta frase?
% Es el mismo código - JJ
%The proposed software has the advantage of full stack JavaScript
%development..
% Ya se ha dicho, ¿no? - JJ
% Si, eso ya quedó - Mario

@@

%Mario: Estaba pensando que otra justificación muy fuerte para el uso de JS sobre plug-ins
%ha sido la seguridad ya que estos presentan otra fuente de vulnerabilidad. Para complicar las cosas a veces (Flash, ActiveX)
%son tecnologías cerradas y propietarias. Por lo menos creo que esas
%fueron las razones que se dieron para eliminar a Flash del iPhone.
% [JJ] Escribe algo...
% [Mario] Ok, aunque va unos párrafos antes.

@@

%El último párrafo podría ser más preciso. Es el único experimento que utiliza recursos heterogeneos
%empleando las tecnologías estándar (JavaScript, JSON, Cookies, etc.) mencionadas previamente.
%[Mario] Ya quedó esto

%Si no se extiende mucho se podría también hablar de la conexión con Cloud Computing,
%se discuten las ventajas de utilizar JavaScript para acceder a recursos donados por voluntarios
%pero falta hablar de como se explotaría el recurso Cloud. Lo digo por el titulo de Volunteers in the Clouds. Tal vez
%se deba hablar de la posibilidad de escalar los sistemas a bajo costo
%o según la demanda.
% Ya se ha hablado. Revísalo - JJ
% Si, ya quedó -Mario

% Si te animas, propón un párrafo - JJ
% Ok, lo escribo. - Mario
% Voy escribiendo algo de HTML5 y Web Workers?, no necesariemente para
% esta sección.
% Para la intro o esta sección - JJ
% Ya se hizo - Mario

>>>>

The rest of the paper is organized as follows: Next we present the
state of the art (Section \ref{sec:soa}) in web-based distributed
computation systems along with attempts to predict and model its behavior. %FERGU: El IEEE es americano
Then, a detailed description of the proposed system is presented
in Section \ref{sec:description}, followed by the experiments and
obtained results in Section \ref{sec:experiments}.
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.

@@

The fulfillment of these properties could be achieved using any of the
languages and associated technologies, mentioned above, provided that the user had
installed the required virtual machine plugin first, but embedding a
ditributed computation client in the browser has the advantage of
providing a single and universal way of accessing resources via an
URI, something that is not guaranteed using desktop
applications. Baratloo et al. tried in 1996 to create a system with
the aforementioned qualities called {\em Charlotte}
\cite{baratloo1996charlotte}. This system, which implemented a
distributed shared memory, was inspired by previous work
on parallel computing systems PVM and MPI and solved most issues by
using the Java virtual machine embedded in the browser,
which provides
security to the user, uniformity of computing environment
independently of the operating system and access to a common data store in the
server. Since the virtual machine is a sandbox, it is safe to the user
and running a compiled bytecode guarantees a certain level of
performance.
 Other issues such as scheduling, which are related to adaptive
 parallelism, are solved on the server. This
paper was later extended and published in a journal in 1999
\cite{baratloo1999charlotte}, but it is interesting to note that
already in the early stages of the web the possibility of
browser-based distributed computing was already researched.

@@

Recent works propose the use of cloud computing services for the components of
client-server distributed EAs. Cloud resources
can reduce operational costs by outsourcing both hardware and software maintenance
to the cloud provider. Another advantage is that they enable the provisioning of computing resources beyond what
is available in most laboratories, allowing researches to
scale algorithms at reasonable costs. Researchers have proposed the use of
public clouds such as Amazon EC2 \cite{CloudScale}, Google App Engine\cite{di2013towards}
and DropBox~\cite{mericloud}. The use of JavaScript to implement
server side components
gives software developers certain advantages in the cloud
paradigm, since is a first-classe citizen
in most Platforms as a Service (PaaS) products as most support the Node.js
framework \cite{wood13:nodejs:paas}. Many web services
have native JavaScript libraries too, and use JSON (JavaScript Object Notation) for data
interchange. Another advantage is that
developers can use the same software tools for both client and server
side development.

@@

In the work presented in this paper, JavaScript has been used throughout the full
stack, which has the advantage of using the self-same lines of code for
writing an evolutionary algorithm for the
desktop or command line and browser clients, both based in the EC
library NodEO \cite{DBLP:conf/gecco/GuervosVGES14}. This saves time % [Mario] Creo que si se debería
% dedicar una oración para recordar la diferencia y relación entre NodIO y NodEO
% En mi mente los digo igual, NodEO como Rodeo y NodIO como Radio y me costó trabajo ver la diferencia
% Pero igual un lector que llegue a leer sin vicios, si vea claramente
% la relación.
% OK, lo hago más adelante - JJ
when writing code and leverages %FERGU: qué diferencias hay entre NodIO y NodEO??
expertise acquired in the library itself. %FERGU: tienes info de LoC
                                %usadas para la sección experimental y
                                %justificar esta frase?
% Es el mismo código - JJ

@@

@@
